Personal Research and Articles

### 2024-05-15 articles.qmd
Update

<p> Jeremy's initial minor infractions soon snowballed into more significant absences. "Each late coming wasn't just about not making it on time; it was about not making it at all," Jeremy explains. The school's response was punitive---detentions that isolated him from his peers and classes, embedding him deeper into the role of a truant. "You're marked, and that marking changes how everyone sees you," he reflects.</p>

@@

>>>>

<p> Jeremy's initial minor infractions soon snowballed into more significant absences. "Each late coming wasn't just about not making it on time; it was about not making it at all," Jeremy explains. The school's response was punitive - detentions that isolated him from his peers and classes, embedding him deeper into the role of a truant. "You're marked, and that marking changes how everyone sees you," he reflects.</p>

@@

<summary> Article 3 <br> <p style="text-align: justify;">

## Under Construction

![](docs/src/images/soon.avif){width="730"}
